When does vapor pressure deficit drive or reduce evapotranspiration?

### 2018-03-19 doc/paper/vpd_et_paper.tex
rejected by GCB, need to do a better job communicating how my approach is new (enabled by medlyn and zhou). preparing for AFM submission now
reformulated g1/gs as ecosystem scale following Medlyn 2017. Fortunately (as expected) doesn't really change story, but will make ecosystem scale derivation much cleaner

% 11/23/2015
\documentclass[draft,linenumbers]{gcbjournal}
% \draftfalse
\usepackage{makecell}
\usepackage{multirow} %AM for tables
\usepackage{booktabs}
\drafttrue

\journalname{Global Change Biology: When does VPD drive or reduce ET?}

@@

\title{When does vapor pressure deficit drive or reduce evapotranspiration?\footnote{Primary Research Article}}

\authors{Adam Massmann\affil{1}, Pierre Gentine\affil{1}, Changjie Lin\affil{1,2}}

\affiliation{1}{Department of Earth and Environmental Engineering, Columbia University, New York, NY 10027}
\affiliation{2}{State Key Laboratory of Hydroscience and Engineering, Department of Hydraulic Engineering, Tsinghua University, Beijing, CN 100084}

>>>>

% 11/23/2015
\documentclass[draft,linenumbers]{agujournal}
% \draftfalse
\usepackage{makecell}
\usepackage{multirow} %AM for tables
\usepackage{booktabs}
\drafttrue

\journalname{Agricultural and Forest Meteorology: When does VPD drive or reduce ET?}

@@

\title{When does vapor pressure deficit drive or reduce evapotranspiration?}

\authors{Adam Massmann\affil{a}, Pierre Gentine\affil{a}, Changjie Lin\affil{a,b}}

\affiliation{a}{Department of Earth and Environmental Engineering, Columbia University, New York, NY 10027}
\affiliation{b}{State Key Laboratory of Hydroscience and Engineering, Department of Hydraulic Engineering, Tsinghua University, Beijing, CN 100084}
